\title{
\vspace{-3ex}
Does God play Tetris? - Team reference document
\vspace{-6ex}}
\date{}
\documentclass[10pt,a4paper]{article}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{fancyhdr}
%\usepackage{fullpage} %should do something but doesn't?
\setlength{\headheight}{13.6pt}
\setlength{\textheight}{692pt}
\pagestyle{myheadings}
\markright{University of Warwick (Does God play Tetris?)\hfill}
\usepackage{listings}
\lstset{
language=Java,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
}

%\usepackage{ifthen}
%
%\newcounter{FileLines}
%\newboolean{RestFile}
%\newcommand{\FileLine}{}
%\newread\File
%
%\newcommand{\CountLinesInFile}[2]
%{
%  \setboolean{RestFile}{true}
%  \setcounter{FileLines}{0}
%
%  \openin\File=#1
%  \whiledo{\boolean{RestFile}}
%  {
%    \ReadNextLine{\File}
%    \ifthenelse{\boolean{RestFile}}{
%      \stepcounter{FileLines}
%    }{}
%  }
%  \closein\File
%}
%
%\newcommand{\ReadNextLine}[1]{
%  \ifthenelse{\boolean{RestFile}}{
%    \read#1 to \FileLine
%    \ifeof#1\setboolean{RestFile}{false}
%    \else % if last line already is read, EOF appears here
%    \fi
%  }{}
%}

\newcommand{\codelisting}[1]{
  \lstinputlisting[emptylines=0]{#1}}

\DeclareMathOperator{\lcm}{lcm}


\begin{document}
\maketitle
\thispagestyle{myheadings}
\section*{Program submission checklist:}
\begin{enumerate}
\item Works on sample inputs given.
\item Works on other sensible inputs.
\item Works on pathological inputs/corner cases.
\item Works in time on the largest possible inputs.
\item Works within memory limit (if given) use -Xmx128m for a limit of 128mb for example.
\item Compiles! (with warnings on! -Xlint)
\item No debug outputs!
\end{enumerate}
\section*{Code}
\subsection*{Big sample}
\lstinputlisting{samplecode.java}

\subsection*{Graphs}
One way of representing
\codelisting{graphsample.java}

Max-Flow
\codelisting{fordfulkerson.java}

Shortest path
\codelisting{shortpath.java}

Min spanning tree
\codelisting{kruskal.java}

Edmonds blossom algorithm for perfect matching (min-weight?)
\codelisting{blossom.java}

DFS/BFS
\codelisting{search.java}

Colouring

Connectivity

Minor testing

Eulerian path

Ham path

\subsection*{Number theory}
GCD
\codelisting{gcd.java}
\[\lcm(a,b) = ab/\gcd(a,b)\]

Sieve of Eratosthenes
\codelisting{seive.java}

\subsection*{Dynamic programming}
Discrete knapsack problem
\codelisting{knapsack.java}

\subsection*{Combinatorics}
Derangements, permutations, other bits

\subsection*{Logic}
2-SAT (requires strongly connected components??)
\codelisting{2sat.java}

\subsection*{Strings}
Matching
\codelisting{kmp.java}


Suffix arrays!
\codelisting{suffix.java}

\subsection*{Geometry}
Centroid of set of point $C = (x_1 + x_2 + \cdots + x_k) / k$.
Centroid of figure, triangulate into right triangles $X_1,\ldots,X_n$ and compute $C_x = (\sum {C_i}_x A_{i})/\sum A_i$, $C_y = (\sum {C_i}_y A_{i})/\sum A_i$ where the centroid of a right triangle perpendicular to the axis is $b/3,h/3$.

Simple data structures
\codelisting{Point.java}

Convex hull, can be used for: furthest points, polygon containment ($P$ inside $Q$ iff $\operatorname{hull}(Q)  = \operatorname{hull}(P\cup Q)$),
\codelisting{convexhull.java}

Closest pair of points
\codelisting{closestpoints.java}


\end{document}
